### 2018-08-08 paper/drafts/draft3.tex
Started the draft 3

\documentclass{article}
\begin{document}

\section{I}

@@

\\

@@

%INtro into the mahoney Paper
Robert Mahoney and Bangura have developed a an estimation algorithm based on the voltage and current that can be sensed by the ESC. While according to their data, they see a reasonable response there is room for improvement. Their algorithm is computationally intense and as well requires a lot of calibration data prior to functioning. This includes the radius, pitch, chord length of the propellor as well as specifications of the motor. We intend to build upon and develop a system that could be simpler and be used on any configuration just as easily.

%Intro into wind sensor
One method of sensing the thrust output of the propellors is to measure the wind output. Like the paper with the pitot tubes, we will have a sensor below the propellors measuring the wind. Unlike a pitot tube, we will use a hot wire anemometer (HWA) wind sensor (WS). The (WS) works on the principle of heating up a coil by running a current through it. As wind passes across it, the wind cools it down. The WS tries to maintain a constant temperature in the coil and the rate of cooling and heating lead to a measure of how much the wind speed is based on a pre-determined calibration. 
\section{II}
%Theory of the mahoney paper

Since we are just focusing on on the static test, there are some assumptions we are making and some math we are skipping.

We are following the math along with the Mahoney Paper.

We have to start by defining the three different velocities that we are measuring.\\

@@

Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say $v_s = v^s_{z}$ and $v_i = v^i_{z}$
What the wind sensor will notice is $v_{tot} = v_{i} + v_{s}$\\

Following along with the mahoney paper we have
\begin{equation}
\lambda = \frac{v_{i} + v_{s}}{\varpi R}
= \frac{v_{i}}{\varpi R}+\frac{v_{s}}{\varpi R}
=\lambda_{i} + \lambda_{s}
\end{equation}

Next we go on to calculate the Thurst relationship with the voltage and current through the equations F1Td and F2Td.

\begin{equation}
T_{d} = \frac{C_{T}}{K^2_{e}}(v_{a} - i_{a}R_{a})
\end{equation}

$K_{e}$ in this case is obtained by calibrating the system and applying a linear regression while $v_{a}, i_{a}, R_{a}$ are all obtained from the power sent to the motor. $C_{T}$ can be calculated by 
\begin{equation}
C_{T} = c_{p} \lambda ^i \lambda 
\end{equation}
\begin{equation}
c_{p} = 2 \rho A R^2 \nonumber
\end{equation}
\begin{equation}
C_{T} = 2 \rho A R^2 \frac{v_{i}}{\varpi R}\frac{v_{i} + v{s}}{\varpi R}  = \frac{2 \rho A (v_{i}^2 + v_{i}v_{s})}{\varpi ^2}
\end{equation}

After calculating these variables we can start to work towards how we control the motor. From the mahoney paper, they individually calculate the appropriate voltage and current to send to the motor. From teh paper to calculate $f_{1}(T_{d})$
\begin{equation}
T_{d} = \frac{C_{T}(v_{a} - i_{a}R_{a})^2}{k_{e}^2}
 = \frac{2 \rho A}{\varpi ^2 k^2_{e}}(v^2_{i} + v_{i}v_{s})(v_{a} - i_{a}R_{a})^2
\end{equation}
$f_{1}(T_{d})$ is used to calculate the voltage. This can be rearranged to obtain $v_{a}$
\begin{equation}
v_{a} = k_{e} \varpi \sqrt{\frac{T_{d}}{2 \rho A (v_{i}^2 + v_{i}v_{s})}} + i_{a}R_{a}
\end{equation}
similarly from the paper we can calculate F2Td where 
\begin{equation}
T_{d} = C_{T} \frac{k_{q}}{C_{Q}}i_{a}
\end{equation}
from applying a similar algebraic reorganization, we get 
\begin{equation}
T_{d} = 2 \rho A \frac{v_{i}^2 + v_{i}v_{s}}{\tau} k_{q}i_a
\end{equation}
from which we can solve for the current and we get
\begin{equation}
i_a = \frac{T_d \tau}{2 \rho A (v_i^2 + v_i v_s) k_q}
\end{equation}
Once these values are calculated, they are sent to the ESC at which point the esc controls the speed of the motor. 
Data from the ESC is collected to help make the thrust estimation. 
Our wind sensor data will be replacing the estimation for the real value which will allow for a more accurate and crisp response.
\end{document}

%Theory of the wind sensor
talk about stream velocity and induced velocity. 
talk about how there is an x,y,z in wind

%How they will be used together
Based on the math above, we will 
\section{III} 
%Proof of the mahoney paper

%Proof of the wind sensor

\section{IV}
%Experimental setup
wind sensor hooked to the ESC so that 2khz speed rather than 50 hz
only doing static test
will do dynamic multirotor test later

>>>>

\documentclass[twocolumn]{article}
\usepackage{subfig}
\begin{document}
	\section{I}

@@

@@

	Robert Mahoney and Bangura have developed a an estimation algorithm based on the voltage and current that can be sensed by the ESC. While according to their data, they see a reasonable response there is room for improvement. Their algorithm is computationally intense and as well requires a lot of calibration data prior to functioning. This includes the radius, pitch, chord length of the propellor as well as specifications of the motor. We intend to build upon and develop a system that could be simpler and be used on any configuration just as easily.

	\section{II}
	%Talk about the theory of the wind.
	%Theory of things like the low pass filter, the algoright, the PID controller, and whatever else we have. Maybe even the statistics
	We have to start by defining the three different velocities that we are measuring.\\

@@

	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say $v_s = v^s_{z}$ and $v_i = v^i_{z}$
	What the wind sensor will notice is $v_{tot} = v_{i} + v_{s}$\\
	\section{III}

	%Proof of the wind sensor
	Graph showing the response of wind sensor and force torque.
	response of rpm based on voltage
	response to blocking. 
	\begin{figure}[h]
	\include{a.png}
	\caption{poop}
	\end{figure}
	\begin{figure}[h]
		\include{dist.png}
		\caption{hello}
	\end{figure}
	\section{IV}
	%Experimental setup
	wind sensor hooked to the ESC so that 2khz speed rather than 50 hz
	only doing static test
	will do dynamic multirotor test later
